---
title: "Getting Started with ShapeToolKit"
author: "Your Name"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with ShapeToolKit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ShapeToolKit)
```

## Introduction

ShapeToolKit is a comprehensive R package for morphometric shape analysis. This vignette will guide you through the basic functionality of the package.

## Shape Analysis

The main function for shape analysis is `shape_analysis()`:

```{r eval=FALSE}
# Analyze shapes in a directory
result <- shape_analysis(
  shape_dir = "path/to/your/shapes",
  norm = TRUE,
  output_file = "analysis_results.xlsx",
  num_pcs = 10
)
```

## Creating Overview Plots

Use `Haug_overview()` to create comprehensive visualization plots:

```{r eval=FALSE}
# Create overview plots
overview <- Haug_overview(
  data = your_data,
  cols = c("PC1", "PC2", "PC3", "PC4"),
  group_col = "species",
  export_pdf = TRUE
)
```

## Interactive Analysis

Launch the Shiny app for interactive analysis:

```{r eval=FALSE}
run_shape_app()
```

## Conclusion

This vignette provides a basic introduction to ShapeToolKit. For more detailed examples and advanced usage, please refer to the function documentation.